Graphs

### 2018-08-24 analysis/shiny/shiny.Rmd
Got Shiny app running.

@@

Scenarios denote a combination of mean function, SNR and variance function. Specifically, each scenario is named as [mean_function].[SNR].[variance_function], where the abbreviations are given by:
Mean function:  
Spikes - sp  
Bumps - bump  
Blocks - blk  
Angles - ang  
Doppler - dop  
Blip - blip  
Corner - cor

@@

On the other hand, we also ran a variety of methods in the simulation study. The methods are abbreviated as follows:  
EbayesThresh - ebayesthresh  
BAMS - bams  
BlockJS - blockjs 
Neighblock - neighblock  
SureShrink - sure  
Bayesian Posterior Mean - postmean  
TI thresholding - tithresh  
SMASH - smash

@@

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
load("res.RData")
scenario_names = as.character(unique(res$scenario))
method_names = as.character(unique(res$method))
#numeric_criteria = names(res)[unlist(lapply(res,is.numeric))]

inputPanel(    
    # Create the checkboxes and select them all by default
    checkboxGroupInput("scen.subset", "Choose Scenarios", 
                        choices  = scenario_names,
                        selected = "sp.1.v2"),

>>>>

NOTE: To launch the Shiny app, run `rmarkdown::run("shiny.Rmd")`

@@

Scenarios denote a combination of mean function, SNR and variance
function. Specifically, each scenario is named as
[mean_function].[SNR].[variance_function], where the abbreviations are
given by:

Mean function:  
Spikes - sp  
Bumps - bump  
Blocks - blk  
Angles - ang  
Doppler - dop  
Blip - blip  
Corner - cor

@@

On the other hand, we also ran a variety of methods in the simulation
study. The methods are abbreviated as follows:

EbayesThresh - ebayesthresh  
BAMS - bams  
BlockJS - blockjs 
Neighblock - neighblock  
SureShrink - sure  
Bayesian Posterior Mean - postmean  
TI thresholding - tithresh  
SMASH - smash

@@

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
load("../../dsc/results/res.RData")
scenario_names = as.character(unique(res$scenario))
method_names = as.character(unique(res$method))

inputPanel(

    # Create the checkboxes and select them all by default
    checkboxGroupInput("scen.subset", "Choose Scenarios", 
                        choices  = scenario_names,
                        selected = "sp.1.v2"),
